Corona of an M7 fast rotator with a high latitude flare

### 2023-04-18 src/tex/ms.tex
[showyourwork] overleaf sync

    \caption{TIC 277539431 (WISEA J105515.71-735611.3)}
    \begin{tabular}{ll}\hline 
         Parameter & Value  \\\hline
         Distance & $13.70\pm0.11\,$pc [2] \\
         $K_s$ mag & $9.666 \pm 0.024$ [3]\\
         $J$ mag & $10.630 \pm 0.023$ [3] \\
         SpT & M7 [1]\\
         Rotation period & $273.618 \pm 0.007\,$min [1]\\
         $v\sin i$ & $38.6\pm1.0\,$km/s [1] \\
         Inclination & $87.0^{+2.0}_{-2.4}\,$ deg [1]\\
         Radius & $0.145\pm0.004\,R_\odot$ [1]\\
         TESS flaring rate $\beta$ &  \\\hline

@@

Ro-Lx relation

>>>>

    \caption{TIC 277539431 (WISEA J105515.71-735611.3)}
    \begin{tabular}{ll}\hline 
         Parameter & Value  \\\hline
         Distance & $13.70\pm0.11\,$pc [2] \\
         $G$ mag & \\
         $G_{BP}$ mag & \\
         $G_{BP}$ mag & \\
         $K_s$ mag & $9.666 \pm 0.024$ [3]\\
         $J$ mag & $10.630 \pm 0.023$ [3] \\
         SpT & M7 [1]\\
         Rotation period & $273.618 \pm 0.007\,$min [1]\\
         $v\sin i$ & $38.6\pm1.0\,$km/s [1] \\
         Inclination & $87.0^{+2.0}_{-2.4}\,$ deg [1]\\
         Radius & $0.145\pm0.004\,R_\odot$ [1]\\
         TESS flaring rate $\beta$ &  \\\hline

@@

\begin{figure}[ht!]
    \script{FIGURE_lx_lbol.py}
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{figures/lx_lbol.png}
        \caption{
         Rossby number versus $L_x/L_{bol}$.
        }
        \label{fig:lxlbol}
    \end{centering}
\end{figure}
